Simulation_Study

### 2022-03-20 Simulation_Study.Rmd
Tests for ar = 0.1, 0.5, and 0.9

```
Let's conduct a simulation study with n = 100, ar = 0.1, and sd = 0.1 (var = 0.01)

@@

@@

@@

@@

@@

>>>>

```
Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1 (var = 0.01). Let's first do this while keeping l = 10 constant.

@@

print(test.data)
```
No clear pattern, but it seems to significantly underestimate the variance on average.

@@

print(test.data)
```
Again, no super clear pattern but it seems to underestimate the variance on average at this range of sample sizes.

@@

The underestimation begins to become far more noticeable around n = 80.

@@

At this range, there seems to be a drop either at n = 70 or n = 50.

@@

Let's try this while keeping the ratio n/l = 10 constant.

for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.5, 0.1, n/10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.5),
     sigma = c(0.1),
     l = c(n/10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.5, 0.1, n/10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.5),
     sigma = c(0.1),
     l = c(n/10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.5, 0.1, n/10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.5),
     sigma = c(0.1),
     l = c(n/10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.5, 0.1, n/10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.5),
     sigma = c(0.1),
     l = c(n/10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(1, 8, 27, 64, 125, 216, 343, 512, 729, 1000, 1331, 1728, 2197, 2744, 3375))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.5, 0.1, n**(1/3), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.5),
     sigma = c(0.1),
     l = c(n**(1/3)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(1, 16, 81, 256, 625, 1296, 2401, 4096))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.5, 0.1, n**(1/4), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.5),
     sigma = c(0.1),
     l = c(n**(1/4)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(1, 32, 243, 1024, 3125, 7776))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.5, 0.1, n**(1/5), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.5),
     sigma = c(0.1),
     l = c(n**(1/5)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, 10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, 10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, 10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, 10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, n/10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(n/10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, n/10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(n/10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, n/10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(n/10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, n/10, m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(n/10),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(1, 8, 27, 64, 125, 216, 343, 512, 729, 1000, 1331, 1728, 2197, 2744, 3375))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, n**(1/3), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(n**(1/3)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(1, 16, 81, 256, 625, 1296, 2401, 4096))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, n**(1/4), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(n**(1/4)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

for(n in c(1, 32, 243, 1024, 3125, 7776))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.9, 0.1, n**(1/5), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.9),
     sigma = c(0.1),
     l = c(n**(1/5)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}
